Extending Height Above Nearest Drainage to Model Multiple Fluvial Sources in Flood Inundation Mapping Applications for the U.S. National Water Model

### 2022-08-21 manuscripts/owp_fim4_2022/reviews/first_review/rebuttal.tex

\begin{reply}
Based on your suggestions, we have significantly improved to the Results section.
The first paragraph briefly introduces the results while the second paragraph gives the reader and in-depth description of the previously numbered Figure 8.
We have made sure all elements of the figure are properly described and that a specific sub-figured is dived into more detail to ensure the reader has a proper understanding of the many elements at play here.
In addition to this enhanced description, we have added a significant amount of information in the third paragraph of the results section that begins to dissect the results and the trends observed in the study.
In a related point and in response to your critique of the Discussion section, we have made significant enhancements to the Discussion section that better elaborate on the material and trends presented in this figure.
We hope that these changes fully address your questions and support this figure that is central to the paper's findings.
\end{reply}

@@

\begin{point}
Fig 6. It seems that the blue areas are inundated areas for the 0.2\% recurrence flow.
How about the inundated areas for the 0.1\% recurrence flow?
I am asking this because the caption mentions 0.2\% and 0.1\%.
Please clarify and revise the figure and caption accordingly. 
\end{point}

\begin{reply}
Reference to 0.1\% recurrence flow was removed in the caption.
There isn't enough granularity to show both the 0.1\% and 0.2\% flows at this scale as they would both look the same.
The main purpose of the figure is to illustrate the spatial extents and distributions of the BLE validation maps.
\end{reply}

\begin{point}
Fig 7. It could be good to add some labels on the figure indicating where this location is within your study area.
What is the mainstem's name?
Would it be possible to add NWM v2.1 catchments to the map?
I understand this might make the figure busy, but I would like to know how many cross sections falls within a NWM catchment?
Is this the FR or MR NWM v2.1 stream or the one you created (GSM)?
\end{point}

\begin{reply}
These names of the rivers are not present in the NWM V2.1 but instead we had to look at their equivalents in the NHDPlusHR stream line data.
While the figure is quite busy, we agree that showing the NWM catchments does provide the reader some sense as to how many BLE cross sections might be associated with a given NWM forecast identifier.
We have updated the caption to include this new layer and provide some more spatial context.
\end{reply}

@@

\begin{point}
Fig 10. Which recurrence event was used to create this inundation map?
Please add this to the caption and mention it in the content where you explain results in Figure 10.
\end{point}

\begin{reply}
We used the 500 yr magnitude and added this to both the caption and in-text content as well.
\end{reply}

@@

\begin{reply}
We have opted for the use of the lower case, Manning's n.
\end{reply}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Begin a new reviewer section
\clearpage
\reviewersection
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{point}
This study presents recent development made by federal agencies and their contractors on streamlining HAND-based flood inundation mapping.
By introducing the idea of level paths, they have also tested the hypothesis that unary stream order networks enhance flood mapping performance skills with HAND.
The study presents some solid work, and the results support their statements.
It's important to expose this workflow, which has been adopted by government agencies in daily operation, to the academic community for broader discussion.
I'm a little concerned about the relevance of this draft.
To publish on Water Resources Research, you need first to highlight the problem you want to solve in water science.
Therefore, presenting some research that is a byproduct of tool development won't interest potential readers of this journal.
The authors may consider reorganizing the draft in a more science-driven way instead of technology.
Based on the reasons above, a major revision is recommended for the editors' consideration.
\end{point}

\begin{reply}
Thank you for taking the time to read our paper and providing ample feedback for improving its content.
We understand your concern and have made every effort to highlight the novel contributions of the manuscript which is an operational, continental scale version of HAND that applies the latest datasets and hydro-conditioning methods while considering multiple sources of fluvial inundation instead of just that of the nearest drainage line.
We hope that the revisions completed based on your suggestions and the suggestions of the other two reviewers better highlight the studies' novel findings in a more science-driven format.
\end{reply}

@@

\begin{point}
Line 82-84 Introducing these two NWM networks in section 1.2 makes more sense.
\end{point}

\begin{reply}
To your point, we have added an additional, high-level explaination of the two stream networks for the NWM in this section to provide the reader with a general idea of what these two illustrated networks mean. 
We did leave some additional detail to be discussed in the NWM section since it is more relevant to that section.
\end{reply}

@@

\begin{point}
Line 112 There isn't a figure 1.2.
\end{point}

\begin{reply}
Fixed.
\end{reply}

\begin{point}
Line 128-129 Here, a statement may be added to explain that running a continental-scale hydrodynamic model regularly is not feasible in operational forecasting, making the simplified alternative like HAND a better solution. (Like line 795-798)
\end{point}

\begin{reply}
Added a sentence specifically mentioning that a continental scale hydrodynamic model is computationally prohibitive.
\end{reply}

\begin{point}
Line 212-230 ``In addition to developed tooling, we introduce research'' I don't like how the authors present the study's purpose. This is not a draft submitted to Environmental Modelling \& Software.
Presenting some research that is a byproduct of tool development won't interest the potential readers of this journal.
\label{pt:science_oriented_purpose}
\end{point}

\begin{reply}
Based on your suggestion, we have rewritten this section to better highlight OWP FIM as a research study and a scientific enhancement.
\end{reply}

@@

\begin{point}
Although very comprehensive, the introduction section seems a little bit long.
This is not a HAND-study review paper, so you don't have to go through all the studies.
The authors may consider removing a few sentences to make it more focused.
\end{point}

\begin{reply}
Several sentences in the introduction of AHPS and NWM were removed to only include the most relevant information to this study.
The section introducing OWP FIM was completely revised to address \ref{pt:science_oriented_purpose} and an entire paragraph on some of the superflous HAND-related studies that are mentioned in the Methods later on was also removed.
\end{reply}

@@

\begin{point}
Figure 2 How are the pruned headwaters derived? Why are they moved away from the original NHDHR endpoints?
\end{point}

\begin{reply}
The first paragraph in original section 2.3.1 was meant to describe the pruning of the NHDPlusHR to better match the resolution of the NWM stream network which was originally derived from the NHDPlus network.
In response to your questions, we have revamped this paragraph to offer the reader a better explanation.
Additionally, we have added more information to the caption of original Figure 2 to provide a better explaination in context.
We hope this level of detail adequately answers your questions.
\end{reply}

\begin{point}
Line 513 I don't think ``work for many instances fine'' is formal enough as a sentence in a scientific journal article.
\end{point}

\begin{reply}
This informal phrase was removed and the sentence was merged with the following sentence.
\end{reply}

@@

\begin{point}
Line 532-533 Four sections have been written in the background before the authors finally dive into the method related to the hypothesis of the current draft, which seems too much.
I appreciate the comprehensiveness, but this is a journal article, not a technical document.
\end{point}

\begin{reply}
Yes we do understand that the methods are quite long but these methods are very much central to the study.
We believe that all methods involved in developing the conclusion of the study should be properly explained or cited.
The methods in the four sub-sections you referenced involve a listing of the primary software dependencies used, description of the datasets used, explanation of the hydro-conditioning processes employed, and a detailing of the derivation of the FIM hydrofabric.
All of these methods are central to the conclusions of the study and must be properly explained here since they have not been published previously.
We argue that keeping these sub-sections intact are required to ensure reproducible, transparent, and open research.
\end{reply}

\begin{point}
Line 544 ``only find an MS stream network of stream order 1 (i.e., headwater)'' From Figure 1, we can tell that most AHPS sites are located on big rivers, which means their stream orders are pretty low.
Then why do you say they are headwater links?
\end{point}

\begin{reply}
We agree this sentence is fairly ambigous so we have clarified this to be more clear.
Yes, typically MS river segments are large rivers with higher Horton-Strahler stream order.
Horton-Strahler stream order starts at order 1 for headwaters and compounds downstream until the outlet point.
However, HAND is computed at the HUC8 spatial resolution for the MS version.
When a mainstem river is clipped to a HUC8 segment, it typically will have an effective stream order of 1 within this particular area.
This is relevant to the computation of HAND as in it removes tributaries that may limit catchment boundary sizes and resulting inundation extents.
We have changed the phrasing to reflect ``uniform stream order'' instead which we believe better describes the circumstances.
\end{reply}

@@

\begin{point}
Figure 4 This figure is confusing and needs some revision.
Demonstrating one network is enough to explain the idea of level paths, but there are a few in this plot.
Also, the annotations are too dense, and their alignment needs to be adjusted.
For example, I'm confused when I see two numbers (6.13 and 10.95) on the left purple link.
How come two numbers there?
\end{point}

\begin{reply}
Based on your appropriate feedback, we have elected to show the same figure but in the context of a HUC12.
Illustrating a HUC12 shows the dendritic structure relevant to the explaination of arbolate sums and level paths (LP).
To be clear, the arbolate sums and LPs were derived at the HUC8 scale but for the figure we only show a HUC12 to show fine grain features more clearly.
The numbers in the figure represent arbolate sums which are cumulative drainage distances of all inclusive upstream reaches.
The arbolate sums are now much more clearly labeled at the whole km value for each reach defined as a junction to junction stream segment.
\end{reply}

@@

\begin{point}
Table 2 \& Figure 8 If only staring at these index numbers and plots, the improvement brought by the current study looks relatively marginal.
The authors may look from other angles to see the benefits brought by analyses with unary stream order networks.
Otherwise, the significance of this study does not look very convincing.
\end{point}

\begin{reply}
We understand that a few metric points may seem like a marginal increase.
In order to better highlight the value of the proposed work, we have changed Table 2 to report the percentage improvement for the proposed models, MS and GMS, when compared to the baseline model, FR.
Each percentage improvement corresponds to a specific metric (CSI, POD, and FAR), magnitude (100 and 500 yr), and Manning's n values (0.06 and 0.12).
These percentage improvements for CSI range from just over 2\% for MS to almost 5\% improvement for GMS which we deem convincing.
Additionally, we argue and highlight that these metrics are for evaluations at the HUC8 scale.
HUC8s are very large regions that aggregate away fine grain results and impacts.
This up to 5\% improvement assessed at a much local scale can seem like a significant improvement.
While the OWP is not currently using an impact based data source such as building footprints or land cover/use maps, viewing the enhancements qualitatively and computing the results at this scale could provide an argument that these results can be significant at the impact scale.
We provided original Figure 10 to highlight the enhancement of this improvement at this scale.
To respond to this point, we have inserted some verbage in the Discussion that acknowledges the limitations of large, HUC8, scale evaluations and hints towards future usage of impact datasets and finer grain evaluations to counter this limitation.
For now, we note an absolute improvement in FIM skill by account for multiple fluvial inundation sources by reducing the scale of HAND computation to utilize stream networks of unit Horton-Strahler stream order.
\end{reply}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Begin a new reviewer section
\clearpage
\reviewersection
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{point}
This paper details the methods employed and findings encountered as the authors endeavored to produce a nationwide flood inundation map (FIM) from National Water Model (NWM) streamflow estimates over the Continental United States.
This is an application of large-domain hydrological modeling.
The relevance of this work to society is not to be understated; a forecast of flood inundation extent and depth from an operational flood forecast model is essential to reducing risks associated with major hydrologic events.
The originality of this work lies in the scale of the problem being addressed and the relevance of operational forecasting to mitigating risk to life and property.

This manuscript adds to the growing body of literature using HAND as a method for determining potential flood inundation in the absence of a full-physics (hydraulic) model.
Ultimately, the process of producing inundation estimates for $>$2.7M stream segments at high spatial resolution ($\sim$10m) is one which required much iteration.
In the end, the authors found that generalizing the stream networks, and using smaller basin areas (HUC8) combined with aggregating individual level-paths yielded better estimates of flood inundation when compared to results from HEC-RAS BLE maps.
Novel methods and computational algorithms were employed along the way, resulting in potentially useful workflows and repositories that readers may follow to produce similar FIMs over the same regions (CONUS).

Although there is a growing body of literature surrounding the use of relative elevation maps such as HAND for flood inundation mapping, this study scales the process to the continental scale and addresses many of the limitations encountered along the way.
Some of the most novel findings in the paper come from the methodological choices employed, such as identifying the appropriate thalweg elevation in the presence of competing channels (DEM-based thalweg vs. hydrography-based thalweg).
Another innovation is in the mosaicking of the FIMs in the presence of tributaries and lower-order streams.
Another very useful innovation lies in ``burning'' levee elevations onto the DEMs to enforce flood control measures on to the HAND surface.
The approach detailed in this manuscript can be seen as a guide for mitigating the 'catchment boundary problem', the importance of which should be emphasized more extensively in this paper.
\label{pt:intro_pt_reviewer_3}
\end{point}

\begin{reply}
We thank you for your overall assessment of the paper and for noting the important contributions this work represents.
While the central scientific contribution of the paper was allowing for multiple fluvial source inundation within HAND based FIMs, we are pleased to hear that the many of the supporting contributions including continental scaling, levee enforcement, open-source software availability, forecasting applications, and thalweg delineation methods were properly conveyed and appreciated.
We hope that the following points in your review are properly addressed to ensure that the main contribution of the paper is properly communicated in a clear and scientific manner to add to the body of literature in this sub-field of hydrology.
\end{reply}

\begin{point}
As a reader, I find the manuscript title and some of the conclusions to be somewhat misdirected.
The idea that Horton-Strahler stream order has a direct impact on the resulting HAND inundation product is misleading.
The stream order of a given reach is determined by the drainage density, and as such is a product of ``upstream'' decisions made during the derivation of the flow network.
Stream order is not an input into the HAND model, nor is it very meaningful when comparing networks that are derived from different headwater locations (such as a pruned version of an existing network such as NHDPlusHR).
Thus, simply reducing stream order should not have any impact on HAND.
There are references in the paper to the impact of drainage density on maximum stream order, but the Conclusions indicate that Horton-Strahler reduction is the reason for improved FIM results, when that reduction is simply an associated result of reduced stream network density.
For example, the authors indicate ``We present two successive methods implemented that reduce drainage densities by reducing Horton-Strahler stream orders of the networks employed...''.
In reality, the reduction Horton-Strahler stream order is the result of, and not the cause for, a reduction in drainage density.
It may be useful to emphasize that the discretization of the network into coherent regions based on level-path or the regionalization methods (such as using HUC8 boundaries), as well as the priority queue calculation (Equation 6) during the HAND raster mosaic process has a bigger impact on the result than the Horton-Strahler number of the network employed.
\end{point}

\begin{reply}
We acknowledge that the original messaging in the paper maybe confusing.
We note in this reply that as described in the methodology surrounding datasets and stream network enforcement as well as your mention \ref{pt:intro_pt_reviewer_3}, stream network is indeed used as an input in our process to compute HAND.
We differ from previous studies mentioned in the paper that utilize accumulated drainage pixels across the entire processing area then threshold those accumulations to produce a stream thalweg network.
In our methods, we consider a forecast network, that of the NWM, and a network that better agrees with the DEM employed, NHDPlusHR Burnlines, to help enforce drainage in the processing unit which is one of the fundamental assumptions and requirements of HAND.
We then use select headwater points to seed a new stream thalweg network that is heavily influenced by the burning and conditioning operations inspired by the input networks, NWM and NHDPlusHR.
The thalweg datum used to detrend or normalize elevations away from mean sea level to that of nearest drainage is thus a product of input stream networks.

Where we believe our explaination lacked, and with respect to your point, is we failed to properly communicate that discretizing the Full Resolution NWM stream network into either Mainstems (MS) network or independent level paths doesn't change the maximum Horton-Strahler stream order or the drainage density.
It does, however, change the effective maximum stream order used in each independent computation of HAND.
This distinction is not properly conveyed in the paper and could lead readers to be confused as to what is actually happening.
In response to this ambigiouty, we have added language in the Stream Order Reduction sub-section of the Methods to ensure this distincition is more clear.

Most notably, we propose a title change to the paper to ensure that the primary objective of considering multi-source fluvial inundation is properly highlighted.
The new proposed title ``Extending Height Above Nearest Drainage to Model Multiple Fluvial Sources in Flood Inundation Mapping Applications for the U.S. National Water Model'' better accounts for the primary purpose of the paper while not allowing an ambigouty to settle in without proper explanation to occur first.
We hope these changes better account for the fundamental contributions of the paper and convey them in a much more clear manner.
\end{reply}

### 2022-08-21 manuscripts/owp_fim4_2022/reviews/first_review/rebuttal.tex

\begin{point}
Another limitation in the methodology lies in using synthetic rating curves (SRCs) that result from reach-averaged geometry parameter derived from the AGREE-DEM (a hydro-conditioning process).
This results in an artificially impacted cross-section and bathymetry structure.
The parameters used to constrain the AGREE method will have a profound impact on the SRCs derived from that DEM due to the excavation process in the AGREE method.
\end{point}

\begin{reply}
We agree with you that the AGREE DEM proceduce does introduce a significant amount of bathymetric manipulation that affects SRC and FIM extent quality.
To your point, we have noted this limitation in multiple sections throughout the paper including the methods, discussion, and conclusions to ensure that the reader is fully aware of this limitation and its effects.
We do motivate future work in this realm as SRC quality is of primary importance to FIM skill.
We invite future researchers to investigate factors that contribute to SRC quality including Manning's n localization as well as bathymetry assimiliation, estimation, and calibration.
Unfortunately, the scope of this article is already too extensive to go much further.
\end{reply}

\begin{point}
Further revision could include a more thorough description of how using level-paths eliminates the catchment boundary problem, when each level path may have many tributaries (and thus multiple catchment boundaries).
There is a bit of missing information in Section 2.5.2 that is necessary for understanding how the catchment boundary problem is mitigated.
It seems that the way around the catchment boundary problem is to calculate HAND for a given level-path while leaving tributaries out of the analysis, and allowing the mosaic process to result in a HAND/FIM result with more extensive coverage over catchment boundary areas.
\end{point}

\begin{reply}
We agree that the original submission lacked sufficient detail as to how the catchment boundary problem is mitigated by level path disaggregation for HAND computation.
We have completely revamped this section to ensure the core contribution of this paper is properly explained.
Additionally, we have introduced a new Figure 7 that better describes how the catchments are delineated at the level path scale as well as the associated inundation.
We hope these considerable changes better communicate this critical section of the paper.
\end{reply}

\begin{point}
The manuscript is, in places, difficult to understand due in part to the large number of acronyms and persistent jargon that pervades it.
There are also many grammatical and syntactical errors that should be edited before re-submission.
The attached annotated manuscript contains many suggestions for resolving these issues along with other comments and feedback, which the authors may find helpful.
For this reason and those outlined above, I suggest to return the manuscript to the author for these (minor) revisions to increase the clarity of the methods and significance of the methodological choices on the results.
\end{point}

\begin{reply}
We have gone through your attached annotated manuscript and have made every effort to address every concern listed.
For any annotations that require an additional response, we provide those below referencing the original line numbers those annotations occur. 
\end{reply}

\begin{point}
L98 - Does the AHPS have a coarser resolution than NWM?
\end{point}

\begin{reply}
AHPS only has two forecast horizons while NWM has three forecast horizons and one analysis product (lookback).  
These are now accounted for in the new manuscript.
\end{reply}

\begin{point}
L368 - 375:
Why does this need to be done?
Is there often a conflict after running AGREE between the DEM thalweg and the AGREE-DEM thalweg?
Depending on the smooth-drop parameter used in AGREE, I wouldn't think there would be any parallel channels in the resulting DEM.
\end{point}

\begin{reply}
The citations in the manuscript refer to the parallel streams problem that arises by using AGREE DEM.
The AGREE DEM enforces a hydrography based streamline and associated notch while not considering some semblemce of the thalweg that might be occuring natively in the DEM.
This creates the notion of a parallel stream when comparing two different DEMs, the AGREE one and the native, unconditioned one.
Additionally, this step provides native elevations to be fed into the thalweg breaching algorithm as opposed to the vastly artificial values in the sharp drop portion of AGREE.
To your point, we have attempted to better explain this in the manuscript.
\end{reply}

\begin{point}
L454: Couldn't you just use the value from the flow accumulation grid at each thalweg pixel rather than derive catchments at each thalweg pixel?
\end{point}

\begin{reply}
The term ``contributing area'' is ambigious here.
We seek to clarify that we are not computing the contributing area in some square km value.
We are just trying the derive catchments or unique drainage polygons for two separate circumstances.
We have changed the language here to bring about more clarity.
\end{reply}

\begin{point}
L478: perimeter?
\end{point}

\begin{reply}
In the reach averaged version of the Manning's Equation, wetted perimeter in the traditional Manning's Equation is translated to bed area given the consideration to the reach length, L, in the formula as well.
\end{reply}

\begin{point}
L491: 0.05 does not appear to be used later. How did the authors decide to use 0.06 and 0.12?
\end{point}

\begin{reply}
In our evaluations, we have noted better general performance with higher Manning's n values thus selected the value of 0.06 from the Djokic work as our baseline.
\end{reply}

\begin{point}
L498: NWM channel parameters, for consistency with the source model? These parameters exhibit variability and have been evaluated during mdoel testing.
\end{point}

\begin{reply}
We tried those parameters and unfortunately they do not yield better results in terms of FIM.
It's possible that those regionalized values are not optimal for FIM purposes as they are tuned more for 1D hydralic routing purposes.
It's likely that lack of accurate bathymetric information interacts heavily with the optimal Manning's n value which is only supposed to account for roughness.
We are keen on working more with the combined effects of bathymetry and roughness parameters to optimize the SRCs for better FIM performance.
In the meantime, we focused on the core contributions of this paper already presented.
\end{reply}

\begin{point}
L684:  This is a key finding of this research and could be emphasized more perhaps in the abstract or conclusions.
\end{point}

\begin{reply}
This key finding has now been further elaborated on in the conclusions and abstract sections.
\end{reply}

\begin{point}
L765-767: I thought lower stream order produced better FIM maps?
\end{point}

\begin{reply}
This sentence is referring to an issue associated with conflation or cross-walking of the FR version of HAND.
This has now been specified so the reader understands that it is likely improved with the new GMS version that ignores neighboring tributaries thus less susceptible to cross-walking errors.
\end{reply}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% references and end document
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
